### 2021-02-06 README.Rmd
Fix #25

Zonebuilder builds on the `sf` package and works well with mapping packages such as `ggplot2`, `leaflet`, `mapdeck`, `mapview` and `tmap`, the last of which we'll use in the following maps.
Attaching the package provides the example datasets `london_area` and `london_cent`, the geographic boundary and the centre of London:

```{r}
library(zonebuilder)
library(tmap)
tm_shape(london_area) + tm_borders() + tm_shape(london_cent) + tm_dots("red")
```

@@

```{r}
london_zones = zb_zone(london_cent, london_area)
zb_plot(london_zones)
```

@@

```{r fig.height=3}
par(mfrow=c(1,3))
zb_plot(zb_doughnut(london_cent, london_area, n_circles = 5), title = "Doughnuts")
zb_plot(zb_segment(london_cent, n_segments = 20), title = "Segments")
zb_plot(zb_zone(london_cent, n_circles = 4, n_segments = 4), title = "4 segments, 4 circles")
```

<!-- tmap_arrange( -->
<!--   zb_view(zb_doughnut(london_cent, london_area, n_circles = 5), title = "Doughnuts"), -->
<!--   zb_view(zb_segment(london_cent, n_segments = 20), title = "Segments") -->
<!--  ) -->

>>>>

Zonebuilder builds on the `sf` package and works well with mapping packages such as `ggplot2`, `leaflet`, `mapdeck`, `mapview` and `tmap`, the last of which we'll use in the following maps.
Attaching the package provides the example datasets `london_a()` and `london_c()`, the geographic boundary and the centre of London:

```{r}
library(zonebuilder)
library(tmap)
tm_shape(london_a()) + tm_borders() + tm_shape(london_c()) + tm_dots("red")
```

@@

```{r}
london_zones = zb_zone(london_c(), london_a())
zb_plot(london_zones)
```

@@

```{r fig.height=3}
par(mfrow=c(1,3))
zb_plot(zb_doughnut(london_c(), london_a(), n_circles = 5), title = "Doughnuts")
zb_plot(zb_segment(london_c(), n_segments = 20), title = "Segments")
zb_plot(zb_zone(london_c(), n_circles = 4, n_segments = 4), title = "4 segments, 4 circles")
```

<!-- tmap_arrange( -->
<!--   zb_view(zb_doughnut(london_c(), london_a(), n_circles = 5), title = "Doughnuts"), -->
<!--   zb_view(zb_segment(london_c(), n_segments = 20), title = "Segments") -->
<!--  ) -->
